---
title: "Introduction to Data Science - HW 2"
author: "Adnres Jimenez- `flastname@floridapoly.edu`"
output: html_notebook
---



# Problem 1 (30 points)

During class you completed an activity in which you practiced `git` commands and operations (such as forking a repository, cloning it using `git clone`, and uploading changes using `git push`).

In this exercise you are asked to modify the `flpoly_student.md` file you worked during class, and format it using the **markdown** tools discussed in class. You must **create a table** that shows the courses you are currently enrolled in, using for the headers of the table: 

- Prefix: in bold letters (such as **COP**)
- Number: in bold letters (such as **2073**)
- Name: in italics (such as _Introduction to Data Science_)
- Credits (such as 3)

a. Make sure your GitHub repo (`practice-repo/`) shows the results of your updated file (remember to use the commands `git add .` , `git commit -m "YOUR MESSAGE"`, and `git push`) 

b. Include a link to your GitHub repo in this document.
[this is the link to the repo](https://github.com/captainspace168/practice-repo.git)

c. Take a screenshot of the GitHub repo, add the screenshot file to the repo, and include it in this document (review how to insert a picture using markdown)
![this is a screenshot of the repo](2021-07-18 (2).png)

# Problem 2 (30 points)

For this problem, you are asked to create a list of **3 concepts** you have learned about so far this semester. Include the name of the course as a sub-heading (that is, using `##`), and the concepts as an unordered list. Include a link to information about at least one of the concept you listed (for example a link to the Wikipedia page about that concept/topics).

_Edit this `.Rmd` file to include the solutions here._
```{r}
# Install the `stringr` package. Only needs to be done once per computer

# Load the package

```


# Problem 3 (40 points)

In this problem you will practice some basic R operations. Include solutions to each items by inserting a new R chunk of code (make sure you run the chunk so that the output is displayed)

(a) Create a variable called `my_name` that contains your preferred name.
```{r}

my_name <- "andres jimenez "
# print test
my_name 

```

(b) Create a variable called `name_length` that holds how many letters are in `my_name`.
```{r}
my_name <- "andres jimenez "
name_length <- nchar(myname)
#print test
name_length

```
(c) Show which value is bigger: $e^\pi$ or $\pi^e$. 
```{r}
val1 <- exp(pi)
#val1
val2 <- pi^exp(1)
#val2
if(val1 > val2){
  print("e^pi is greater")
}else{
print("pi^e is greater")  
}
  

```
(d) Define a function called `add_tree` that takes a single argument and returns a value 3 times larger than the input.
```{r}
add_tree <- function() {
  argument = readline(prompt= "enter a number to recove a value 3 times larger : ")
  argument = as.integer(argument)
  print(argument*3)
} 
add_tree()
```
(e) Use the colon operator `:` to create a vector `v` of numbers from 10 to 49. Find the length of this vector using the `length()` function.
```{r}
v <- 10:49
#v
length(v)
```
(f) Use the `seq()` function to produce a range of number from -5 to 10 in 0.5 increments.
```{r}
seq(-5, 10, by = 0.5)
```


