---
title: "Basic Operations in R"
output: html_notebook
---

_Problems adapted from the PSDS textbook_

## Calling built-in functions

Create a variable `my_name` that contains your name

```{r}
my_name <- 'andres jimenez'
my_name 

```


Create a variable `name_length` that holds how many letters (including spaces) are in your name (use the `nchar()` function)

```{r}
name_length <- nchar(my_name)
```



Print the number of letters in your name

```{r}
name_length

```

Create a variable `now_doing` that is your name followed by "is programming!" (use the `paste()` function)

```{r}
now_doing <- paste(my_name, 'is programming!')
now_doing
```

Make the `now_doing` variable upper case

```{r}
toupper(now_doing)

```


## Operations with Numbers

Pick two of your favorite numbers (between 1 and 100) and assign them to variables `fav_1` and `fav_2`

```{r}
fav1 <- 10
fav2 <- 20


```


Divide each number by the square root of 201 and save the new value in the original variable

```{r}
fav1<- fav1/sqrt(201)

fav2 <- fav2/sqrt(201)


```


Create a variable `raw_sum` that is the sum of the two variables. Use the `sum()` function for practice.

```{r}
raw_sum <- sum(fav1,fav2)
raw_sum
```


Create a variable `round_sum` that is the `raw_sum` rounded to 1 decimal place. Use the `round()` function.

```{r}
round_sum <- round(raw_sum)
round_sum

```


Create two new variables `round_1` and `round_2` that are your `fav_1` and `fav_2` variables rounded to 1 decimal places

```{r}
round1 <- round(fav1)
round2 <- round(fav2)
```

Create a variable `sum_round` that is the sum of the rounded values

```{r}
sum_round <- sum(round1+round2)
sum_round
```


Which is bigger, `round_sum` or `sum_round`? (You can use the `max()` function!)

```{r}
max(sum_round, round_sum)
if(sum_round == round_sum){
  print('sum_round and round_sum are equal')
}else if(sum_round > round_sum){
  print('sum_round is larger')
}else{
  print('round_sum is larger')
}
```


## Functions and Conditionals

Define a function `is_twice_as_long` that takes in two character strings, and returns whether or not (e.g., a boolean) the length of one argument is greater than or equal to twice the length of the other.
_Hint_: compare the length difference to the length of the smaller string


```{r}
is_twice_as_long <- function(length1, length2){
  if(nchar(length1) == 2*nchar(length2)|nchar(length1) >= nchar(length2)){
   boolean<- isTRUE(TRUE)
    paste('length1 is twice as long or greather than  length2:',boolean)
  }else if(nchar(length2) == 2*nchar(length1)|nchar(length2) >= nchar(length1)){
    boolean<- isTRUE(TRUE)
    paste('length2 is twice as long or greather than  length1:', boolean)
  }else{
    boolean<- isTRUE(TRUE)
   paste('neither is twice as long as the other:',boolean) 
  }
}


```

Call your `is_twice_as_long` function by passing it different length strings to confirm that it works. Make sure to check when _either_ argument is twice
as long, as well as when neither are!

```{r}
is_twice_as_long('hello','hi')
is_twice_as_long('hi','good afternoon')






```

Define a function `describe_difference` that takes in two strings. The function should return one of the following sentences as appropriate 

- "Your first string is longer by N characters"

- "Your second string is longer by N characters"

- "Your strings are the same length!"

```{r}
describe_difference <- function(st1, st2){
  st1<-nchar(st1)
  st2<-nchar(st2)
  total1<- st1 -st2 
  total2<- st2 - st1 
  if(st1 > st2 ){
    paste('your first string is longer by', total1 )

  }else if(st2>st1){
    paste('your second string is longer by', total2)
  }else if(st1==st2){
  print ('both string are the same length')
    
  }else{
    print('something is wrong check your input')
  }
}


```



Call your `describe_difference` function by passing it different length strings to confirm that it works. Make sure to check all 3 conditions

```{r}
describe_difference('hello ','how are you')
describe_difference('how is your day going','how have you been ')
describe_difference('hi','hi')
```


